Enhance Image Classification Performance

### 2021-04-18 A-BasicCommom/CICAI2021/image_classification.tex
1. fix some writeup.

  Unsupervised pre-training is important to modern research of deep learning.
  Lee et al.~\cite{lee2009convolutional} used the pre-training approaches in Computer Vision tasks in 2009,
  and, Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary, which can be omitted in some cases, in the Computer Vision tasks later from 2010 to 2016,
  However, it started to flourish since Mikolov et al.~\cite{mikolov2013distributed} had proposed Word2Vec in the natural language processing,
  recently, Devin et al.~\cite{devlin2019bert}'s BERT language model dominates in most tasks in natural language processing.
  The pre-training approach in natural language processing is close resemble to Vicent et al.~\cite{vincent2008extracting}'s Denoising Autoencoder model initially designed for images processing.
  Thus, the pre-training step becomes important in CV and NLP.

@@

  Chen et al.~\cite{chen2020generative} trained image representation by sequence Transformers and tested on CIFAR-10 to show it is outperforming to Wide-ResNet
which was inspired by unsupervised natural language representation learning.
  Wang et al.~\cite{wang2019development} reviewed that convolutional neural networks had been proposed in the 1960s, and had its implementation in the 1980s,
and until LeCun et al.~\cite{lecun1990handwritten}'s first experiment on handwritten digit recognition, CNN's great potential had been revealed.
  In the 2010s, Krizhevsky et al.~\cite{krizhevsky2012imagenet} proposed the deep architecture, AlexNet, by concatenating multiple components of CNN layers.
Several years later, a lot of variants of AlexNet had been proposed by researchers and the accuracy of ImageNet had been greatly improved, e.g. ZFNet~\cite{zeiler2014visualizing}, VGG~\cite{simonyan2014very}, GoogLeNet~\cite{szegedy2015going}, ResNet~\cite{he2016deep},
  ResNeXt~\cite{xie2017aggregated}, inception-ResNet-v2~\cite{szegedy2016inception}, DenseNet~\cite{huang2016deep}.
  Lu and Weng~\cite{lu2007survey} concluded that for the multi-source image classification tasks, additional information such as signatures, texture, context, and ancillary data can be combined to achieve better performance.
And it is difficult in handling the dichotomy between pixels and natural language texts in a single model. For per-pixel approach, non-parametric classifiers, e.g. neural networks, support vector machines, and decision trees,
are the most well-known algorithms for their performance and generalization advantages in the late 1990s and 2000s.
  Cui et al.~\cite{cui2020revisiting} proposed several whole-word-masking pre-trained Chinese language models,
which are improved versions of BERT~\cite{devlin2019bert} pre-trained language models, namely RoBERTa(3), RoBERTa-L(3), and RoBERTa-L(24). The training of the RoBERTa(3) language model was based on Devlin et. al.'s BERT model,
moreover, the pre-trained Chinese language models use extra 5 billion training tokens comparing to 0.4 billion tokens in the BERT model.
These models achieved better performance in Chinese machine reading comprehension, Chinese document classification, and other downstream natural language tasks.
  He and Peng~\cite{he2017fine} combined the vision stream and language stream as two parallel channels for extracting multi-source information in the image classification task,
and tested on the CUB-200-2011 image dataset and achieved $85.55\%$ by combining GoogLeNet~\cite{szegedy2015going} and CNN-RNN~\cite{reed2016learning}, the result outperformed many competitors.
  Fern{\'a}ndez et al.~\cite{fernandez2014we} compared different classifiers in small datasets, and they found that the random forest algorithm ranks first among the 179 classifiers.
  Recall that Kim~\cite{kim2014convolutional} had proved that unsupervised pre-trained language model $word2vec$ and CNN outperformed many other machine learning algorithms,
e.g. support vector machines and conditional random field, in many datasets such as movie reviews, Stanford sentiment treebank, and TREC question.
Cui et al.'s pre-trained language model, namely RoBERTa(3), RoBERTa-L(3), and RoBERTa-L(24), had improved performances over many other machine learning algorithms.
BERT and RoBERTa-L(24) models both achieved an f1-score of 97.8\% in the THUCNews dataset, which contains 65,000 news reports in 10 domains.

@@

We use the Jittor\cite{hu2020jittor} library as the modeling tool, and the TsinghuaDogs\cite{Zou2020TsinghuaDogs} dataset to compare the performance with competitors.The experiment was performed on an Nvidia V100, with 16GB of RAM,
which can provide 100 tera-flops of computation capability.

@@

\par Three of the most popular approaches for image classification tasks are per-pixel, subpixel, and heterogeneous.
CNN models are fundamental and often used as baselines to compare the classification performance.
The vision system of human has a mechanism that focuses limited attention on the key information to save resources and to get the most efficient information quickly.
Before introduction of the Attention mechanism, there was a problem in RNN that long distances of information would be weakened,
just as people with weak memory could not remember the past.

@@

Generality speaking, the performance of the pre-trained language models achieved in the document classification tasks.

@@

For the per-pixel image classification approach, for every RGB channel of pixels in an image,
each pixel had its pixel-channel code, ranging from 0x00 to 0xff for different colors.
Thus, taking these pixels in an image is resembled to ASCII characters in a document.
An experiment show that document classification capability can be transferred to image classification naturally.

\begin{figure*}
\begin{center}
  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{classification.pdf}}
\end{center}
   \caption{Concatenation, encoder, representation, and extraction layers for image classification task.}
\label{fig:short}
\end{figure*}

We design simple classification models without too many layers, as Figure (1) shows,
and use the CIFAR-10 and CIFAR-100 dataset as an example to show the architecture of the model.
The model architecture has seven functional layers:

\begin{itemize}
\item {\bf Input layer}
\item {\bf Concatenation layer}
\item {\bf Trim layer}
\item {\bf Encoder layer}
\item {\bf Embedding layer}
\item {\bf Feature Extraction layer}
\item {\bf Output layer}
\end{itemize}

@@

\begin{figure*}
\begin{center}
  \fbox{\rule{0pt}{0in} \includegraphics[width=0.9\linewidth]{image-classification(3).pdf}}
\end{center}
   \caption{Accuracy of the image classification models with the pre-trained language encoder on the CIFAR-10 and CIFAR-100 dataset in the training epochs.}
\label{fig:short}
\end{figure*}

>>>>

  \par Unsupervised pre-training is important to modern research of deep learning.
  Lee et al.~\cite{lee2009convolutional} used the pre-training approaches in Computer Vision tasks in 2009,
  and, Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary, which can be omitted in some cases, in the Computer Vision tasks later from 2010 to 2016,
  However, it started to flourish since Mikolov et al.~\cite{mikolov2013distributed} had proposed Word2Vec in the natural language processing,
  recently, Devin et al.~\cite{devlin2019bert}'s BERT language model dominates in most tasks in natural language processing.
  The pre-training approach in natural language processing is close resemble to Vicent et al.~\cite{vincent2008extracting}'s Denoising Autoencoder model initially designed for images processing.
  Thus, the pre-training step becomes important in CV and NLP.

  \par The presentation of the Transformer~\cite{vaswani2017attention} model has profoundly changed the field of NLP,
especially the subsequent series of Transformer-based large-scale pre-training language models,
which opened a new model training paradigm in NLP: first in large-scale unlabeled Pre-train the model on the text,
and then use task-specific small data to fine-tune the model.

  \par Transformer's first show in CV is Vision Transformer~\cite{dosovitskiy2020image}.
The specific method is to divide a picture into multiple non-overlapping patches.
The patch here can be considered as a token in NLP, and the patches are arranged to form a sequence, get patches embedding after a Linear Embedding.
In order to do the image classification task, it is still imitating the BERT method of adding $[CLS]$, adding a special mark $[class]$ at the beginning of the patch sequence, and then add the position code to the Transformer to do the encoding.

  \par Liu et al.~\cite{liu2021swin} uses a patch merge mechanism between the Transformer layers to integrate adjacent patch features to achieve an effect similar to the downsampling in CNN.
In ViT, self-attention is calculated for all input patches, and the shifted window mechanism designed by Liu et al. allows self-attention to be calculated only for patches in a certain local window for the complexity problem of Transformer.
The window should be shifted to the lower right corner, this achieves cross-window feature interaction, which makes up for the limitation that only a single window can be seen.
To a certain extent the receptive field is expanded on the upper side. The design is to have two successive Transformer layers, one using regular windows, and the other using sliding windows.

@@

  Chen et al.~\cite{chen2020generative} trained image representation by sequence Transformers and tested on CIFAR-10 to show it is outperforming to Wide-ResNet
which was inspired by unsupervised natural language representation learning.
  Wang et al.~\cite{wang2019development} reviewed that convolutional neural networks had been proposed in the 1960s, and had its implementation in the 1980s,
and until LeCun et al.~\cite{lecun1990handwritten}'s first experiment on handwritten digit recognition, CNN's great potential had been revealed.
  In the 2010s, Krizhevsky et al.~\cite{krizhevsky2012imagenet} proposed the deep architecture, AlexNet, by concatenating multiple components of CNN layers.
Several years later, a lot of variants of AlexNet had been proposed by researchers and the accuracy of ImageNet had been greatly improved, e.g. ZFNet~\cite{zeiler2014visualizing}, VGG~\cite{simonyan2014very}, GoogLeNet~\cite{szegedy2015going}, ResNet~\cite{he2016deep},
  ResNeXt~\cite{xie2017aggregated}, inception-ResNet-v2~\cite{szegedy2016inception}, DenseNet~\cite{huang2016deep}.
  Lu and Weng~\cite{lu2007survey} concluded that for the multi-source image classification tasks, additional information such as signatures, texture, context, and ancillary data can be combined to achieve better performance.
And it is difficult in handling the dichotomy between pixels and natural language texts in a single model.
For per-pixel approach, non-parametric classifiers, e.g. neural networks, support vector machines, and decision trees,
are the most well-known algorithms for their performance and generalization advantages in the late 1990s and 2000s.
 \par Cui et al.~\cite{cui2020revisiting} proposed several whole-word-masking pre-trained Chinese language models, which are improved versions of BERT~\cite{devlin2019bert} pre-trained language models.
The pre-trained Chinese language models use extra 5 billion training tokens comparing to 0.4 billion tokens in the BERT model. BERT and RoBERTa-L(24) models both achieved an f1-score of 97.8\% in the THUCNews dataset.
  He and Peng~\cite{he2017fine} combined the vision stream and language stream as two parallel channels for extracting multi-source information in the image classification task,
and tested on the CUB-200-2011 image dataset and achieved $85.55\%$ by combining GoogLeNet~\cite{szegedy2015going} and CNN-RNN~\cite{reed2016learning}, the result outperformed many competitors.
  Fern{\'a}ndez et al.~\cite{fernandez2014we} compared different classifiers in small datasets, and they found that the random forest algorithm ranks first among the 179 classifiers.
  Recall that Kim~\cite{kim2014convolutional} had proved that unsupervised pre-trained language model $word2vec$ and CNN outperformed many other machine learning algorithms,
e.g. support vector machines and conditional random field, in many datasets such as movie reviews, Stanford sentiment treebank, and TREC question.

@@

We use the Jittor\cite{hu2020jittor} library as a modeling tool to compare with competitors on the TsinghuaDogs\cite{Zou2020ThuDogs} dataset.
The experiment was conducted on the Nvidia V100 with a memory of 16GB which provides 100 Tera-Flops computing power.

@@

\par CNN models are fundamental and often used as baselines to compare the classification performance.
The vision system of human has a mechanism that focuses limited attention on the key information to save resources and to get the most efficient information quickly.
Before introduction of the Attention mechanism, there was a problem in RNN that long distances of information would be weakened,
just as people with weak memory could not remember the past.

@@

@@

\par For the per-pixel image classification approach, for every RGB channel of pixels in an image,
each pixel had its pixel-channel code, ranging from 0x00 to 0xff for different colors.
Thus, taking these pixels in an image is resembled to ASCII characters in a document.
An experiment show that document classification capability can be transferred to image classification naturally.

\begin{figure*}
\begin{center}
  \fbox{\rule{0pt}{0in} \includegraphics[width=0.95\linewidth]{classification.pdf}}
\end{center}
   \caption{Concatenation, encoder, representation, and extraction layers for image classification task.}
\label{fig:short}
\end{figure*}

\par We design simple classification models without too many layers, as Figure (1) shows,
and use the CIFAR-10 and CIFAR-100 dataset as an example to show the architecture of the model.
The model architecture has seven functional layers: Input layer,
Concatenation layer,
Trim layer,
Encoder layer,
Embedding layer,
Feature Extraction layer,
Output layer.

@@

\begin{figure*}
\begin{center}
  \fbox{\rule{0pt}{0in} \includegraphics[width=0.9\linewidth]{image-classification(3).pdf}}
\end{center}
   \caption{Accuracy of the image classification models with the pre-trained language encoder on the CIFAR-10/10 and COVID-19 dataset in the training epochs.}
\label{fig:short}
\end{figure*}
